Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-11-30 paper/paper.tex
More algorithm

\begin{corollary}
    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\V(G)$, and edges between vertices $p$ and $q$ if there are at least $n$ simple paths of
    length exactly $\ell$ between $p$ and $q$ in $G$. Then any $k$-less subgraph isomorphism
    $P \lessnonind{k} T$ induces a new $k$-less subgraph isomorphism
    $P^{n+k, 2}\lessnonind{k} T^{n, 2}$ using the same vertex assignments.
\end{corollary}

@@

        \loopcomp{\mathcal{T}}) \textnormal{~only if we want induced\label{line:comp}},$

@@

            \nl $D_v \gets \{ w \in D_v : $ \\

@@

        \nl $D_v \gets D_v \cup k~\textnormal{distinct wildcard values}$

@@

    \nl $D_v \gets \textnormal{the smallest domain in}~D$ \;

@@

In lines ?? we use the reasoning from \cref{section:degreefiltering} to eliminate infeasible initial
values from the domains. We do not use iterated label filtering \citep{constraints10} to recalculate
neighbourhood degree sequences if any vertices are not present in any target domain after
construction: preliminary experiments indicated that this happened very rarely on our instances.

To handle unmapped vertices, on line ?? we include $k$ additional wildcard $\bot$ values in each
domain (rather than a single value which may be used $k$ times).

@@

?? Describe supplemental graphs. These are also used for eliminating infeasible values.

If no effectively-unit domains remain, we attempt stronger propagation for the all-different
constraint. Our $\FuncSty{allDifferent}$ function is the bit-parallel propagator taken from
\citet{DBLP:conf/cp/McCreeshP15}, and is \emph{not} the usual matching-based propagator ?? cite
which guarantees generalised arc consistency. Because we use multiple wildcard values, we do not
need to modify the algorithm to allow a single wildcard value to be used more than once. ?? a bit
more on how it works?. It can easily be seen that this propagator will always find Hall sets or
failed Hall sets of size zero or one, but it may miss larger sets. This propagation could create new
effectively-unit domains; if so, we loop.

If propagation is unable to prove unsatisfiability, we search. We pick the smallest domain (line
??), and try giving it each of its remaining values in turn. We use the value the ordering heuristic
from the original algorithm; wildcards are treated as having degree zero, in an attempt to
maximising the expected number of solutions remaining during search
\citep{DBLP:conf/ijcai/McCreeshPT16}.  We introduce a symmetry break (line~\ref{line:sym}) to try
only a single wildcard value for each variable.

>>>>

\begin{corollary}\label{corollary:supplemental}
    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\V(G)$, and edges between vertices $p$ and $q$ if there are at least $n$ simple paths of
    length exactly $\ell$ between $p$ and $q$ in $G$. Then any $k$-less subgraph isomorphism
    $P \lessnonind{k} T$ induces a new $k$-less subgraph isomorphism
    $P^{n+k, 2}\lessnonind{k} T^{n, 2}$ using the same vertex assignments.
\end{corollary}

@@

            \loopcomp{\mathcal{T}}) \textnormal{~only if we want induced\label{line:comp}}, \label{line:supplemental}$

@@

            \nl $D_v \gets \{ w \in D_v : $ \label{line:degreefiltering} \\

@@

        \nl $D_v \gets D_v \cup k~\textnormal{distinct wildcard values} \label{line:wildcards}$

@@

    \nl $D_v \gets \textnormal{the smallest domain in}~D$ \label{line:pickd} \;

@@

In line~\ref{line:degreefiltering} we use the reasoning from \cref{section:degreefiltering} to
eliminate infeasible initial values from the domains. We do not use iterated label filtering
\citep{constraints10} to recalculate neighbourhood degree sequences if any vertices are not present
in any target domain after construction: preliminary experiments indicated that this happened very
rarely on our instances.

To handle unmapped vertices, on line~\ref{line:wildcards} we include $k$ additional wildcard $\bot$
values in each domain (rather than a single value which may be used $k$ times).

@@

We deal with the additional constraints discussed in \cref{section:pathfiltering} by constructing
supplemental graphs, as in the \citet{DBLP:conf/cp/McCreeshP15} algorithm. This is done on
line~\ref{line:supplemental}: the variable $L$ contains a list of pattern / target pairs, and
following \cref{corollary:supplemental}, we will search for a mapping which is simultaneously a
subgraph isomorphism between every pair in this list. We also do degree-based reasoning using each
of these graph pairs.

If no effectively-unit domains remain, we attempt stronger propagation for the all-different
constraint. Our $\FuncSty{allDifferent}$ function is the bit-parallel propagator taken from
\citet{DBLP:conf/cp/McCreeshP15}, and is \emph{not} the usual matching-based propagator
\citep{DBLP:conf/aaai/Regin94} which guarantees generalised arc consistency. Because we use multiple
wildcard values, we do not need to modify the algorithm to allow a single wildcard value to be used
more than once. ?? A few sentences on how this works. It can easily be seen that this propagator
will always find Hall sets or failed Hall sets of size zero or one, but it may miss larger sets.
This propagation could create new effectively-unit domains; if so, we loop.

If propagation is unable to prove unsatisfiability, we search. We pick the smallest domain
(line~\ref{line:pickd}) and try giving it each of its remaining values in turn. We use the value the
ordering heuristic from the original algorithm; wildcards are treated as having degree zero, in an
attempt to maximising the expected number of solutions remaining during search
\citep{DBLP:conf/ijcai/McCreeshPT16}.  We introduce a symmetry break (line~\ref{line:sym}) to try
only a single wildcard value for each variable.
